### 2015-09-14 Irregular-occ/Irregular-occ.tex
.

As explicited in section \ref{Sec: introducao}, there is no consensus on a single model about the region where the irregular satellites were formed. \cite{Cuk2004} showed that the progenitor of the Himalia group may have origin in heliocentric orbits similar to the Hilda asteroid group.

Phoebe, the most studied irregular satellite, was identified by \cite{Clark2005} that its surface is probably covered by material of cometary origin. It was also stated by \cite{Johnson2005} that if the porosity of Phoebe would be of about 15\%, Phoebe would have an uncompressed density similar to those of Pluto and Triton.

@@

Making a new model for the orbits of these objects would demand a lot of time and delay the publication of predictions of possible events to occur in the very near future. Thus, we utilized the positions obtained by \cite{GomesJunior2015} to identify error patterns in the ephemeris. The error patterns in right ascension and in declination could be used to extrapolate the offsets to the satellite ephemeris by the time of the predicted occultation, improving it. Plots of the offsets over true anomaly (see Fig. \ref{Fig:offxtanom} for declination offsets of Carme, for instance) clearly show the systematic errors in the JPL ephemeris.

@@

\begin{figure*}
\begin{centering}
\subfigure[Offset from the JPL ephemeris]{\includegraphics[scale=0.25]{figures/DEC_anom.png} \label{Fig:offxtanomxjpl}}
\subfigure[\textcolor{red}{Offset from the numerical integration}]{\includegraphics[scale=0.25]{figures/DEC_anom.png} \label{Fig:offxtanomxni}}
\caption{Offsets of the declination of Carme by true anomaly from the JPL ephemeris and \textcolor{red}{from the numerical integration from the positions obtained in \cite{GomesJunior2015}}.}
\end{centering}
\end{figure*}

@@

A total of 588 events \textcolor{red}{(Não estou contando ainda os eventos para Tritão)} were identified between January 2015 and December 2017. Table \ref{Tab: occ-list} exemplifies the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{Consertar tabela}}
\begin{centering}
\begin{tabular}{ccccccccccccccccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
d m Year & h m s & \multicolumn{2}{c}{RA (ICRS) Dec} & C/A & P/A & v & D & R* & $\lambda$ & LST & $\Delta e_{\alpha *}$ & $\Delta e_{\delta}$ & pm & ct & $E_{\alpha *}$ & $E_{\delta}$ & $\mu_{\alpha *}$ & $\mu_{\delta}$ \tabularnewline
\hline
 07 10 2015 & 21 52 34. &  10 53 40.1835 & +08 21  00.489 & 0.465 & 200.31 & 39.31 & 6.25 & 16.6 & 179. & 09:48 & -31.0 & -13.0 & ok & uc &   0  &  0 & -13 &  -7 \tabularnewline
 23 10 2015 & 07 54 50. &  11 05 26.6037 & +07 14  32.030 & 1.017 & 201.33  & 36.11 & 6.12 & 15.5 & 16. & 08:59 & -31.0 & -13.0 & ok & uc &  0  &  0 &  -7 &  -4 \tabularnewline
 31 10 2015 & 00 24 19. &  11 10 56.2964 & +06 42  07.110 &  1.801 &  21.84 & 33.94 &  6.04 & 16.9 &  123. & 08:34 & -31.0 & -13.0 & ok & uc & 0  &  0 & -4 & -13 \tabularnewline
 07 11 2015 &  21 22 53. &  11 16 14.3041 & +06 10  05.194 &  0.306 &  202.36 & 31.33 & 5.94 & 16.2 & 162. & 08:09 & -31.0 & -13.0 & ok & uc & 0 & 0 & 0 & 0 \tabularnewline
 08 11 2015 & 04 27 21. &  11 16 25.7881 & +06 08  55.566 & 1.077 & 202.38 & 31.23 & 5.94 & 16.9 & 55. & 08:08 & -31.0 & -13.0 & ok & uc & 0 & 0 & 9 & -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates of the satellite (corrected the computed ephemeris offset derived in Sec. \ref{Sec: Offset}); C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$: computed offsets in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

@@

\begin{figure*}
\begin{centering}
\subfigure[Nominal prediction]{\includegraphics[width=8.8cm]{figures/Himalia_nominal.eps}  \label{Fig: occ-Himalia-nooff}}
\subfigure[\textcolor{red}{Offset de Himalia a partir do ajuste}]{\includegraphics[width=8.8cm]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[Observation at February 22 (different FOVs)]{\includegraphics[width=8.8cm]{figures/Himalia_22fev.eps}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[Observation at March 03 (same FOV)]{\includegraphics[width=8.8cm]{figures/Himalia_03mar.eps}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the nominal prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. The straight lines show the size of the shadow. \ref{Fig: occ-Himalia-nooff} is the map using the nominal positions of the star and satellite. \ref{Fig: occ-Himalia-ajuste} shows the shadow given an estimated offset for the position of Himalia related to the JPL ephemeris obtained in section \ref{Sec: Offset}. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias. \textcolor{red}{Figura b será mudada após confirmarmos o offset para Himalia}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015. \textcolor{red}{Tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
Nominal & 00:39:25 UTC & $0\farcs714$ \tabularnewline
Offset &   & \tabularnewline
Feb. 22 Obs. & +12s & -33mas (109km) \tabularnewline
Mar. 03 Obs. & -10s & -19mas (61km)\tabularnewline
\hline
\end{tabular}
\par\end{centering}

@@

\begin{table}
\caption{\label{Tab: comparison-Elara} Comparison between the predictions of Elara occultation at March 30, 2015. \textcolor{red}{Tem que ver direito o offset do ajuste}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A  \tabularnewline
\hline
Nominal & 01:45:15 UTC & $1\farcs139$ \tabularnewline
Offset &  & \tabularnewline
Mar. 25 Obs. & -59 s & -17mas (61km) \tabularnewline
Apr. 02 Obs. & +15 s & -89mas (307km) \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}

@@

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017.}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke & 22 & 12 & 16 & 50 \tabularnewline
Carme & 25 & 20 & 14 & 59 \tabularnewline
Elara & 32 & 14 & 16 & 62 \tabularnewline
Himalia & 25 & 15 & 12 & 52 \tabularnewline
Lysithea & 22 & 16 & 11 & 49 \tabularnewline
Pasiphae & 26 & 19 & 20 & 65 \tabularnewline
Sinope & 19 & 15 & 21 & 55 \tabularnewline
\hdashline
Phoebe & 13 & 32 & 98 & 143 \tabularnewline
\hdashline
Nereid & 41 & 11 & 1 & 53 \tabularnewline
Triton &  &  &  &  \tabularnewline
\hline
\end{tabular}
\par \end{centering}
Occultations predicted using the UCAC4 catalogue. For Nereid and Triton, the occultations in 2015 and 2016 were predicted using the WFI catalogue as explained in Sec. \ref{Sec: predictions}.
\end{table}

>>>>

As explicited in section \ref{Sec: introducao}, there is no consensus on a single model about the region where the irregular satellites were formed. \cite{Cuk2004} showed that the progenitor of the Himalia group may have origin in heliocentric orbits similar to the Hilda asteroid group. \cite{Sheppard2005} stated that the irregular satellites may be some of the objects that were formed within the giant planets region. \cite{Sheppard2005} and \cite{Jewitt2007} also expose the possibility for the irregular satellites having their origin as comets or similar to the TNOs.

Phoebe, the most studied irregular satellite, was identified by \cite{Clark2005} that its surface is probably covered by material of cometary origin. It was also stated by \cite{Johnson2005} that if the porosity of Phoebe would be of about 15\%, which the authors believe it is possible, Phoebe would have an uncompressed density similar to those of Pluto and Triton.

@@

Making a new model for the orbits of these objects would demand a lot of time and delay the publication of predictions of possible events to occur in the very near future. Thus, we utilized the positions obtained by \cite{GomesJunior2015} to identify error patterns in the ephemeris. The error patterns in right ascension and in declination could be used to extrapolate the offsets to the satellite ephemeris by the time of the predicted occultation, improving it. Plots of the offsets over true anomaly (see Fig. \ref{Fig:offxanom} for declination offsets of Carme, for instance) clearly show the systematic errors in the JPL ephemeris.

@@

\begin{figure*}
\begin{centering}
\subfigure[Offset from the JPL ephemeris]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxjpl}}
\subfigure[\textcolor{red}{Offset from the numerical integration}]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxni}}
\caption{Offsets of the declination of Carme by true anomaly from the JPL ephemeris and \textcolor{red}{from the numerical integration of the positions obtained in \cite{GomesJunior2015}}.
\label{Fig:offxanom}}
\end{centering}
\end{figure*}

@@

A total of 588 events \textcolor{red}{(Not counting Triton's event yet)} were identified between January 2015 and December 2017. Table \ref{Tab: occ-list} exemplifies the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{I still have to fix the table}}
\begin{centering}
\begin{tabular}{ccccccccccccccccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
d m Year & h m s & \multicolumn{2}{c}{RA (ICRS) Dec} & C/A & P/A & v & D & R* & $\lambda$ & LST & $\Delta e_{\alpha *}$ & $\Delta e_{\delta}$ & pm & ct & $E_{\alpha *}$ & $E_{\delta}$ & $\mu_{\alpha *}$ & $\mu_{\delta}$ \tabularnewline
\hline
 07 10 2015 & 21 52 34. &  10 53 40.1835 & +08 21  00.489 & 0.465 & 200.31 & 39.31 & 6.25 & 16.6 & 179. & 09:48 & -31.0 & -13.0 & ok & uc &   0  &  0 & -13 &  -7 \tabularnewline
 23 10 2015 & 07 54 50. &  11 05 26.6037 & +07 14  32.030 & 1.017 & 201.33  & 36.11 & 6.12 & 15.5 & 16. & 08:59 & -31.0 & -13.0 & ok & uc &  0  &  0 &  -7 &  -4 \tabularnewline
 31 10 2015 & 00 24 19. &  11 10 56.2964 & +06 42  07.110 &  1.801 &  21.84 & 33.94 &  6.04 & 16.9 &  123. & 08:34 & -31.0 & -13.0 & ok & uc & 0  &  0 & -4 & -13 \tabularnewline
 07 11 2015 &  21 22 53. &  11 16 14.3041 & +06 10  05.194 &  0.306 &  202.36 & 31.33 & 5.94 & 16.2 & 162. & 08:09 & -31.0 & -13.0 & ok & uc & 0 & 0 & 0 & 0 \tabularnewline
 08 11 2015 & 04 27 21. &  11 16 25.7881 & +06 08  55.566 & 1.077 & 202.38 & 31.23 & 5.94 & 16.9 & 55. & 08:08 & -31.0 & -13.0 & ok & uc & 0 & 0 & 9 & -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\textbf{Notes}. Entries included: day of the year and UTC time of the prediction; right ascension and declination of the occulted star - in the original table, these coordinates are immediately followed by the geocentric astrometric equatorial coordinates of the satellite (corrected the computed ephemeris offset derived in Sec. \ref{Sec: Offset}); C/A: the geocentric closest approach, in arcseconds; P/A: the planet position angle with respect to the occulted star at C/A, in degrees; velocity in plane of sky, in km s$^{-1}$: positive = prograde, negative = retrograde; D: planet range to Earth, in AU; R*: normalized magnitude to a common shadow velocity of 20 km s$^{-1}$ by the relationship $\textrm{Mag}* = \textrm{Mag}_{\textrm{actual}} + 2.5 \times \log 10 \left(\frac{\textrm{velocity}} {20 \textrm{km}\, \textrm{s}^{-1}} \right)$. A value of 50.0 means that the star is not in the 2MASS; $\lambda$: east longitude of subplanet point in degrees, positive towards east; LST: UT + $\lambda$: local solar time at subplanet point, hh:mm; $\Delta e_{\alpha *}$ and $\Delta e_{\delta}$: computed offsets in mas applied to the ephemeris right ascension and declination, respectively; pm: ok = proper motion applied, no = no proper motion applied; catalogue cross-identification (ct) = uc (UCAC2), 2m (2MASS), fs (field star); $E_{\alpha *}$ and $E_{\delta}$: uncertainties (mas) in right ascension and declination. A value of 9999 means that there was no estimation of the respective uncertainty; $\mu_{\alpha *}$ and $\mu_{\delta}$: proper motions in right ascension and declination, respectively (mas/year).
\label{Tab: occ-list}
\end{table*}

@@

\begin{figure*}
\begin{centering}
\subfigure[Nominal prediction from JPL]{\includegraphics[width=8.8cm]{figures/Himalia_nominal.eps}  \label{Fig: occ-Himalia-nooff}}
\subfigure[\textcolor{red}{From the numerical integration}]{\includegraphics[width=8.8cm]{figures/Himalia2_2015-03-03T00:39:18.png}  \label{Fig: occ-Himalia-ajuste}}
\subfigure[Observation at February 22 (different FOVs)]{\includegraphics[width=8.8cm]{figures/Himalia_22fev.eps}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[Observation at March 03 (same FOV)]{\includegraphics[width=8.8cm]{figures/Himalia_03mar.eps}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the nominal prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. The straight lines show the size of the shadow. \ref{Fig: occ-Himalia-nooff} is the map using the nominal positions of the star and satellite. \ref{Fig: occ-Himalia-ajuste} shows the shadow given an estimated offset for the position of Himalia related to the JPL ephemeris obtained in section \ref{Sec: Offset}. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias. \textcolor{red}{Figure b waiting for the offset of Himalia}}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015. \textcolor{red}{Waiting for the right offset}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
Nominal & 00:39:25 UTC & $0\farcs714$ \tabularnewline
Offset &   & \tabularnewline
Feb. 22 Obs. & +12s & -33mas (109km) \tabularnewline
Mar. 03 Obs. & -10s & -19mas (61km)\tabularnewline
\hline
\end{tabular}
\par\end{centering}

@@

\begin{table}
\caption{\label{Tab: comparison-Elara} Comparison between the predictions of Elara occultation at March 30, 2015. \textcolor{red}{Waiting for the right offset}}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from nominal prediction} \tabularnewline
Method  & Instant of C/A  & C/A  \tabularnewline
\hline
Nominal & 01:45:15 UTC & $1\farcs139$ \tabularnewline
Offset &  & \tabularnewline
Mar. 25 Obs. & -59 s & -17mas (61km) \tabularnewline
Apr. 02 Obs. & +15 s & -89mas (307km) \tabularnewline
\hline
\end{tabular}
\par\end{centering}
\end{table}

@@

\begin{table}
\caption{\label{Tab: satellite-occultation} Number of stellar occultations for each satellite from 2015 up to 2017.}
\begin{centering}
\begin{tabular}{lcccc}
\hline  \hline
%\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & 2015  & 2016 & 2017 & Total \tabularnewline
\hline
Ananke & 22 & 12 & 16 & 50 \tabularnewline
Carme & 25 & 20 & 14 & 59 \tabularnewline
Elara & 32 & 14 & 16 & 62 \tabularnewline
Himalia & 25 & 15 & 12 & 52 \tabularnewline
Lysithea & 22 & 16 & 11 & 49 \tabularnewline
Pasiphae & 26 & 19 & 20 & 65 \tabularnewline
Sinope & 19 & 15 & 21 & 55 \tabularnewline
\hdashline
Phoebe & 13 & 32 & 98 & 143 \tabularnewline
\hdashline
Nereid & 41 & 11 & 1 & 53 \tabularnewline
Triton &  &  &  &  \tabularnewline
\hline
\end{tabular}
\par \end{centering}
Occultations predicted using the UCAC4 catalogue. For Nereid and Triton, the occultations in 2015 and 2016 were predicted using the WFI catalogue as explained in Sec. \ref{Sec: predictions} \textcolor{red}{Numbers of Triton yet to be written}.
\end{table}
